A Bioconductor workflow for processing and analysing spatial proteomics data

### 2018-04-03 main.tex
add f1000 files

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}

@@

%% Uncomment this lines for superscript citations instead
% \usepackage[super]{natbib}

@@

\usepackage{hyperref}

@@

\title{\textit{F1000Research} Article Template}
\titlenote{The title should be detailed enough for someone to know whether the article would be of interest to them, but also concise. Please ensure the broadness and claims within the title are appropriate to the content of the article itself.}
\author[1,2]{Lisa M. Breckels}
\author[1,2]{Laurent Gatto}
\affil[1]{Computational Proteomics Unit, Cambridge Systems Biology Centre, University of Cambridge, Tennis Court Road, Cambridge, CB2 1GA, UK}
\affil[2]{Cambridge Centre for Proteomics, Department of Biochemistry, University of Cambridge, Tennis Court Road, Cambridge, CB2 1GA, UK}

@@

\begin{abstract}
Abstracts should be up to 300 words and provide a succinct summary of the article. Although the abstract should explain why the article might be interesting, care should be taken not to inappropriately over-emphasise the importance of the work described in the article. Citations should not be used in the abstract, and the use of abbreviations should be minimized. 
\end{abstract}

\clearpage

\include{bioc-workflow}

>>>>

%% \documentclass[10pt,a4paper,twocolumn]{article}
\documentclass[10pt,a4paper]{article}
\usepackage{f1000_styles}

@@

%% Uncomment this lines for superscript citations insteadl
% \usepackage[super]{natbib}

@@

\usepackage{hyperref}
\usepackage{framed}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{knitr}
\usepackage{alltt}

\definecolor{fgcolor}{rgb}{.5,.6,.7}

\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}

\newcommand{\Rpackage}[1]{\textsl{#1}}
\newcommand\Biocpkg[1]{%
  {\href{http://bioconductor.org/packages/#1}%
    {\Rpackage{#1}}}}
\newcommand\Biocannopkg[1]{\Biocpkg{#1}}
\newcommand\Biocexptpkg[1]{\Biocpkg{#1}}

@@

\title{A Bioconductor workflow for processing and analysing spatial proteomics data}

% \titlenote{The title should be detailed enough for someone to know
% whether the article would be of interest to them, but also
% concise. Please ensure the broadness and claims within the title are
% appropriate to the content of the article itself.}

\author[1,2]{Lisa M. Breckels}
\author[2]{Claire M. Mulvey}
\author[2]{Kathryn S. Lilley}
\author[1,2]{Laurent Gatto}
\affil[1]{Computational Proteomics Unit, Cambridge Systems Biology Centre, University of Cambridge, Tennis Court Road, Cambridge, CB2 1GA, UK}
\affil[2]{Cambridge Centre for Proteomics, Department of Biochemistry, University of Cambridge, Tennis Court Road, Cambridge, CB2 1GA, UK}

@@

\begin{abstract}
\input{abstract}
\end{abstract}

\input{bioc-workflow}

\bigskip

{\small\bibliographystyle{unsrtnat}
\bibliography{bibliography}}
